### 2013-03-28 doc/sosp13/evaluation.tex
fix context switching

Figure~\ref{fig:context-switch-exp} shows the average context switch time as
the number of workers grow. There are two important takeaway points from these
data. Context switch time for the number of workers we use ($\approx$1K workers) is
on the order of 50 ns; and prefetching has significant impact on context
switch time. And context switch time does not grow significantly with the
number of workers --- even with one-half million workers, context switch
is around 75ns.

We also measured (not in the plot) the \emph{rate} of context switch for all
cores in a node, which showed that our rate is limited by off-chip memory
bandwidth. Each context is 4 cache lines (1 for the worker struct and 3 for
stack data), leading to 8 cache line transfers per context switch
(write the previous context, read the next in). The off-chip bandwidth of a
single socket in our system is 270M cache lines per second, which implies that
we can sustain at most 34M context switches per second per socket, which is
almost exactly what we sustain.

>>>>

Figure~\ref{fig:context-switch-exp} shows the average context switch time as
the number of workers grow. There are two important takeaway points from these
data. Context switch time for the number of workers we use ($\approx$1K workers) is
on the order of 50 ns; and prefetching has significant impact on context
switch time. And context switch time does not grow significantly with the
number of workers --- even with one-half million workers, context switch
is around 75ns. In comparison, for the same yield test using kernel-level
Pthreads on a single core, the switch time is 450ns for a few threads and 800ns for
1000-32000 threads.

If we calculate aggregate context switch\emph{rate} of all
cores in a node, we find that with prefetching, \Grappa context
switching is
limited \emph{not} by memory latency, as normally assumed, but rather memory bandwidth.
Specifically, we emprically found that 4 cachelines (1 for worker
struct and 3 for stack data) was sufficient to avoid cache misses in
the microbenchmark. Every context switch then requires 8 cacheline transfers. The off-chip
bandwidth of a single socket in our system is 270M cachelines per
second \cite{porterfield:bw,Nelson:hotpar11-real}. This implies that
we can sustain at most 34M context switches per second per socket once
the space of all contexts is enough to mostly reside outside of L3.
